Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-11-26 patchy-selection-paper.tex
figs

To test the robustness of our results to the various approximations we used,
we used individual-based simulations on a one-dimensional lattice of 501 demes,
run for 25,000 generations.
More details are given below in \nameref{ss:simulations},
and the number of simulations used and parameter values are given in supplementary tables \ref{stab:mutation_params} and \ref{stab:migration_params}.
To estimate the mean time until adaptation by mutation,
we used one centrally located patch of 99 demes
and a mutation rate of $\mu=10^{-5}$,
and to estimate the mean time until adaptation by migration,
we used two centrally located patches of 99 demes
separated by a varying number of demes,
with one patch initialized to have the $B$ allele at frequency 0.8.
In each case, we measured the ``time to adaptation'' as the amount of time until at least 100 $B$ alleles
were present in the previously unadapted patch.
Figure~\ref{fig:sim_times}
summarizes how the results compare to theory,
excluding parameter combinations where a majority of simulations did not adapt by 25,000 generations
or the patch was not large enough to support a stable population of $B$ alleles.

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(A)} 
      Time until adaptation by mutation in an isolated patch for different parameter combinations,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (as $1/\mutrate$, horizontal axis).
      \textbf{(B)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate} (as $1/\migrate$, horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:migration_params} and \ref{stab:mutation_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
  }   \label{fig:sim_times}
\end{figure}

@@

\input{mutation-parameters-table.tex}

\input{migration-parameters-table.tex}

>>>>

To test the robustness of our results to the various approximations we used,
we used individual-based simulations on a one-dimensional lattice of 501 demes,
run for 25,000 generations.
More details are given below in \nameref{ss:simulations},
and the number of simulations used and parameter values are given in supplementary tables \ref{stab:mutation_params} and \ref{stab:migration_params}.
To estimate the mean time until adaptation by mutation,
we used one centrally located patch of 99 demes
and a mutation rate of $\mu=10^{-5}$,
and to estimate the mean time until adaptation by migration,
we used two centrally located patches of 99 demes
separated by a varying number of demes,
with one patch initialized to have the $B$ allele at frequency 0.8.
In each case, we measured the ``time to adaptation'' as the amount of time until at least 100 $B$ alleles
were present in the previously unadapted patch.
Figure~\ref{fig:sim_times}
summarizes how the results compare to theory,
excluding parameter combinations where a majority of simulations did not adapt by 25,000 generations
or the patch was not large enough to support a stable population of $B$ alleles.
Supplementary figures \ref{sfig:sim_mutation_times} and \ref{sfig:sim_migration_times}
show all times, 
and depictions of typical simulation runs are shown in supplementary figures
\ref{sfig:} .

The agreement is reasonable for both

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(left)} 
      Time until adaptation by mutation in an isolated patch for different parameter combinations,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (horizontal axis).
      \textbf{(right)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate} (horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:migration_params} and \ref{stab:mutation_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
  }   \label{fig:sim_times}
\end{figure}

@@

Here we provide additional details regarding the simulations we used
to validate the theory in figures \ref{fig:sim_times} and \ref{fig:sim_probs}.

% table of parameters, produced by analyze-sims.R
\input{mutation-parameters-table.tex}

% table of parameters, produced by analyze-sims.R
\input{migration-parameters-table.tex}

% example trace plots
